<<<<<<< HEAD
---
title: "Penguins"
author: "Sally Heo"
date: "3/1/2022"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    theme: darkly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Intro

Today we are going to work with the penguin data to learn *RMarkdown*.

# Load Libraries

```{r message=FALSE, warning=FALSE}
library(tidyverse) # Load tidyverse
library(here) # Load here
library(palmerpenguins) # Load palmer penguins
```

# Inspect the data
```{r}
glimpse(penguins) # Look at Palmer Penguins data
```

# Make a plot

```{r, warning=FALSE, message=FALSE}
penguins %>% # Using penguin dataset # Penguin dataframe
  ggplot(aes(x = bill_length_mm,# Length
             y = bill_depth_mm,#depth 
             color = species))+ #color with species
  geom_point()+ # Adding geometry point
  geom_smooth(method = "lm")+ # Adding linear method (linear line)
  labs(x = "Bill Length (mm)", # Labeling x-axis Bill Length
       y = "Bill Depth (mm)")+ # Labeing y-axis Bill Depth
  theme_bw() # Theme black and white
  
```

=======
---
title: "Penguins"
author: "Sally Heo"
date: "3/1/2022"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    theme: darkly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Intro

Today we are going to work with the penguin data to learn *RMarkdown*.

# Load Libraries

```{r message=FALSE, warning=FALSE}
library(tidyverse) # Load tidyverse
library(here) # Load here
library(palmerpenguins) # Load palmer penguins
```

# Inspect the data
```{r}
glimpse(penguins) # Look at Palmer Penguins data
```

# Make a plot

```{r, warning=FALSE, message=FALSE}
penguins %>% # Using penguin dataset # Penguin dataframe
  ggplot(aes(x = bill_length_mm,# Length
             y = bill_depth_mm,#depth 
             color = species))+ #color with species
  geom_point()+ # Adding geometry point
  geom_smooth(method = "lm")+ # Adding linear method (linear line)
  labs(x = "Bill Length (mm)", # Labeling x-axis Bill Length
       y = "Bill Depth (mm)")+ # Labeing y-axis Bill Depth
  theme_bw() # Theme black and white
  
```

>>>>>>> 0637edba3d05df5a14b7b74aa7151407f9d54e07
