<<<<<<< HEAD
---
title: "Week6_Homework"
author: "Sally Heo"
date: "3/3/2022"
output: 
  prettydoc::html_pretty:
    theme: hpstr
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, fig.path = '../Outputs/', message = FALSE)
```

# Introduction #

Today we are going to work with the **Palmer Penguins** data and create a table and figure in _R Markdown_ 

We will be looking at three **Palmer Penguins** species:

* Adelie
* Chinstrap
* Gentoo 

The **Palmer Penguins** were studied on three islands:

* Biscoe
* Dream
* Torgersen

# Load the libraries

First, libraries needed to code are loaded. 

```{r}
library(kableExtra) # Load kableExtra
library(tidyverse) # Load tidyverse
library(here) # Load here
library(palmerpenguins) # Load Palmer Penguins
```

# Inspecting the data

Through glimpse, we can take a quick look at the **Palmer Penguins** dataframe. 

```{r}
glimpse(penguins) # View the Penguins data
```

# Table for Palmer Penguins

Here, we will look at the mean and variance of bill depth (mm) for the Palmer Penguins living on each of the three islands. 

```{r, echo = FALSE}
penguins %>% 
  group_by(species) %>% # Group by species
  summarise(mean = mean(bill_depth_mm, na.rm = TRUE), # Summarise is used to calculate mean bill depth (mm)
           variance = var(bill_depth_mm, na.rm = TRUE)) %>% # calculating variance in bill depth (mm) 
  kbl() %>% # Making it a kable table
  kable_classic() %>% # Using the kable theme classic
  row_spec(0, bold = T, color = "white", background = "dodgerblue") %>% # changing the first row to have bold text and dodgerbue background
  kable_styling(full_width = FALSE) # Making the width smaller than the entire page

```
# Plot

We will make a plot to study Bill Depth (mm) for each of the three species living on each island for each sex (male and female).

```{r Lab6_Homework.png, echo = FALSE}
penguins %>% # Using penguin dataframe
  drop_na(sex, bill_depth_mm) %>% # Dropping NA values from sex and bill depth
  ggplot(mapping = aes(x = sex, # Ploting sex on x-axis
                       y = bill_depth_mm, # Plotting bill depth on y-axis
                       color = species)) + # Plotting color to species
geom_boxplot() + # Making geometry point, box plot
facet_wrap(~island) + # Facet wrapping for island
labs(title = "Bill Depth (mm) vs Sex", # Label title of plot
     subtitle = " Average Bill Depth by Sex for Adelie, Chinstrap, and Gentoo Penguins", # Adding subtitle
     y = "Bill Depth (mm)", # changing y-axis title
     x = "Sex", # changing x-axis title
     caption = "Source: Palmer Station LTER / palmerpenguins package",) + # Adding a caption
  theme(title = element_text(size = 14, color = "darkorchid2")) # Editing theme and font of plot and color

```




=======
---
title: "Week6_Homework"
author: "Sally Heo"
date: "3/3/2022"
output: 
  prettydoc::html_pretty:
    theme: hpstr
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, fig.path = '../Outputs/', message = FALSE)
```

# Introduction #

Today we are going to work with the **Palmer Penguins** data and create a table and figure in _R Markdown_ 

We will be looking at three **Palmer Penguins** species:

* Adelie
* Chinstrap
* Gentoo 

The **Palmer Penguins** were studied on three islands:

* Biscoe
* Dream
* Torgersen

# Load the libraries

First, libraries needed to code are loaded. 

```{r}
library(kableExtra) # Load kableExtra
library(tidyverse) # Load tidyverse
library(here) # Load here
library(palmerpenguins) # Load Palmer Penguins
```

# Inspecting the data

Through glimpse, we can take a quick look at the **Palmer Penguins** dataframe. 

```{r}
glimpse(penguins) # View the Penguins data
```

# Table for Palmer Penguins

Here, we will look at the mean and variance of bill depth (mm) for the Palmer Penguins living on each of the three islands. 

```{r, echo = FALSE}
penguins %>% 
  group_by(species) %>% # Group by species
  summarise(mean = mean(bill_depth_mm, na.rm = TRUE), # Summarise is used to calculate mean bill depth (mm)
           variance = var(bill_depth_mm, na.rm = TRUE)) %>% # calculating variance in bill depth (mm) 
  kbl() %>% # Making it a kable table
  kable_classic() %>% # Using the kable theme classic
  row_spec(0, bold = T, color = "white", background = "dodgerblue") %>% # changing the first row to have bold text and dodgerbue background
  kable_styling(full_width = FALSE) # Making the width smaller than the entire page

```
# Plot

We will make a plot to study Bill Depth (mm) for each of the three species living on each island for each sex (male and female).

```{r Lab6_Homework.png, echo = FALSE}
penguins %>% # Using penguin dataframe
  drop_na(sex, bill_depth_mm) %>% # Dropping NA values from sex and bill depth
  ggplot(mapping = aes(x = sex, # Ploting sex on x-axis
                       y = bill_depth_mm, # Plotting bill depth on y-axis
                       color = species)) + # Plotting color to species
geom_boxplot() + # Making geometry point, box plot
facet_wrap(~island) + # Facet wrapping for island
labs(title = "Bill Depth (mm) vs Sex", # Label title of plot
     subtitle = " Average Bill Depth by Sex for Adelie, Chinstrap, and Gentoo Penguins", # Adding subtitle
     y = "Bill Depth (mm)", # changing y-axis title
     x = "Sex", # changing x-axis title
     caption = "Source: Palmer Station LTER / palmerpenguins package",) + # Adding a caption
  theme(title = element_text(size = 14, color = "darkorchid2")) # Editing theme and font of plot and color

```




>>>>>>> 0637edba3d05df5a14b7b74aa7151407f9d54e07
