---
title: 'Week 8: Functional Programming'
author: "Sally Heo"
date: "3/17/2022"
output:
  prettydoc::html_pretty:
    theme: tactile
          
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Libraries needed to code ##
```{r, message=FALSE, warning=FALSE}
library(tidyverse) #Load tidyverse
library(here) #Load here
library(palmerpenguins) #Load palmerpenguins
library(PNWColors) #Load PNWColors
```
## Data Analysis ##
## Create a dataframe ##
* Creating a dataframe of random numbers
* Anytime you have to do a task more than once
* Example of where we want to rescale data in multiple columns (value - min/(max-min))
```{r}
df <- tibble::tibble(
  a = rnorm(10),
  b = rnorm(10),
  c = rnorm(10),
  d = rnorm(10)
)
head(df)
```

## Rescale every column individually ##
* We can also write a function for this
```{r}
rescale01 <- function(x) {
  value <- (x-min(x, na.rm = TRUE))/(max(x, na.rm = TRUE))/(max(x, na.rm = TRUE)-min(x, na.rm = TRUE))
  return(value)
}
df %>% 
  mutate(a = rescale01(a),
         b = rescale01(b),
         c = rescale01(c),
         d = rescale01(d))
```
## Make function to convert degrees fahrenheit to celcius ##
```{r}
fahrenheit_to_celsius <- function(temp_F){ #Naming the function, decide what arguments are
  temp_C <- (temp_F - 32) * 5 / 9 #Calculation for F to C, Put in the equation
  return(temp_C) #Temp in C is being returned
}
fahrenheit_to_celsius(32) # 32 F to celsius
fahrenheit_to_celsius(212) # 212 F to celsius

```

## Think, Pair, Share ##
### Write a function that converts celcius to kelvin (Remember Kelvin is celcius + 273.15)
```{r}
c_to_k <- function(temp_c) {
  temp_k <- (temp_c + 273.15)
  return(temp_k)}
c_to_k(2)
```

# Making plots into a function #
```{r, message=FALSE, warning=FALSE}
myplot <- function(data, x, y){ #Give name to function, name of function and set up
pal <- pnw_palette("Lake",3, type = "discrete") #my color palette

ggplot(penguins, aes(x = {{x}}, y = {{y}}, color = island)) + #Make names broad so it can be applicable to several values
  geom_point() + #Add a geometry point
  geom_smooth(method = "lm") + #Add a linear model
  scale_color_manual("Island", values = pal)+ #Use pretty colors and change the legend title
  theme_bw() #theme bw
}


myplot(data = penguins, x = body_mass_g, y = bill_length_mm)
myplot(data = penguins, x = body_mass_g, y = flipper_length_mm)
```

## Adding defaults ##
* Create a default for the function to always default to the penguins dataset
* Can set those directly in the function. 

```{r, message=FALSE, warning=FALSE}
myplot <- function(data = penguins, x, y, lines=TRUE){
pal <- pnw_palette("Lake",3, type = "discrete")

if(lines==TRUE){
ggplot(data, aes(x = {{x}}, y = {{y}}, color = island))+
  geom_point()+
  geom_smooth(method = "lm")+
  scale_color_manual("Island", values = pal)+
  theme_bw()
}
else{
ggplot(data, aes(x = {{x}}, y = {{y}}, color = island))+
    geom_point()+
    scale_color_manual("Island", values=pal)+
    theme_bw()
}
}
myplot(x = body_mass_g, y = flipper_length_mm, lines = FALSE)

  
  
myplot(x = body_mass_g, y = flipper_length_mm)+ #Layering the plot using + (like it is a regular ggplot to change things like labels)
  labs(x = "Body mass (g)",
       y = "Flipper length (mm)")
```
## Add an if-else statement for more flexibility ##
* Suppose that if a > b then f should be = to 20, else f should be equal to 10. Using if/else we:
```{r}
a <- 4
b <- 5
if (a > b) { #my question
  f <- 20 #if it is true give me answer 1
} else { #else give me answer 2
  f <- 10
}
f
```
# Back to plotting #
* Using if..else we can make our function even more flexible
* Wanting the option of adding the geom_smooth lines
*We can create a variable that if set to TRUE add the geom_smooth, otherwise print without
```{r}
myplot <- function(data = penguins, x, y, lines = TRUE){ #add new argument for lines
pal <- pnw_palette("Lake",3, type = "discrete") # my color palette

ggplot(data, aes(x = {{x}}, y = {{y}}, color = island))+
  geom_point()+
  geom_smooth(method = "lm")+ #add a linear model
  scale_color_manual("Island", values=pal)+ #use pretty colors and change the legend title
  theme_bw()
}
```

# If-else #
* Adding an if-else statement
```{r, message=FALSE, warning=FALSE}
myplot <- function(data = penguins, x, y, lines = TRUE){ # Add new argument for lines
pal <- pnw_palette("Lake",3, type = "discrete") #My color palette
if(lines==TRUE){
ggplot(data, aes(x = {{x}}, y = {{y}}, color = island))+
    geom_point()+
    geom_smooth(method = "lm")+ #Add a linear model
    scale_color_manual("Island", values = pal)+ #Use pretty colors and change the legend title
    theme_bw()
}
else{
ggplot(data, aes(x = {{x}}, y = {{y}}, color = island))+
    geom_point()+
    scale_color_manual("Island", values=pal)+ #Use pretty colors and change the legend title
    theme_bw()
}
}

myplot(x = body_mass_g, y = flipper_length_mm) #Testing (With lines)
myplot(x = body_mass_g, y = flipper_length_mm, lines = FALSE) #Testing (without)
```

