---
title: "Week 7 Bad Plot/Good Plot Homework"
author: "Sally Heo"
date: "3/14/2022"
output: html_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Introduction ###
Today I will be using the data from [Tidy Tuesday 2019-05-28](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-05-28) on Wine to create a good plot and a bad plot for my homework assignment. 

### Load Libraries ###
First, before creating any ggplots, I will load the libraries that are required to make my ggplots. 

```{r, message=FALSE, warning=FALSE,}
library(tidyverse)#Load tidyverse
library(here) #Load here
library(png) #Load png
library(plotly) #Load plotly
library(tibble) #Load tibble
library(jpeg) #Load jpeg
library(ggpubr) #Load ggpubr
library(readr) #Load readr
library(dplyr) #Load dplyr
```

### Load and View the Wine Data ###
Next, I will load the Wine data to examine which variables in the dataset I would like to work with. After viewing the wine data, I decided to analyze the relationship of the grape type of the wine and the price in USD. 

```{r message=FALSE, warning=FALSE}
wine_ratings <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-05-28/winemag-data-130k-v2.csv")
View(wine_ratings)
```
### Data Wrangling ###
I will do some data wrangling to organize and only filter the variables in the Wine data that I want to work with. Two data frames will be used for plotting. Wine_ratings_bad will be the data frame used for my "bad plot" and wine_ratings_good will the the data frame used for by "good plot". 

### Bad Plot ###
```{r, warning=FALSE, message=FALSE, echo=FALSE}
wine <- here("Week_7", "Data", "wine.jpg") #Importing wine image to use for plot
wine <- jpeg::readJPEG(wine) #Reading the wine image as a jpeg
Wine_ratings_bad <- wine_ratings %>% #Using Wine_ratings_bad dataframe
  select(country, points, price, variety, winery)#Only want to look at these specific variables
Wine_ratings_bad %>% #Wine_ratings_bad dataframe 
  ggplot(aes(x = variety,#Plot x-axis as variety
             y = price, #Plot y-axis as price
             color = price)) + #Fill color for the price
  background_image(wine) + #Using background image of wine
  geom_line()+ #Using geometry line
  theme(axis.ticks = element_blank(), #Remove axis ticks
        axis.text.y = element_blank(), #Remove y-axis text
        axis.title.y = element_blank()) + #Hiding y-axis title
  theme(panel.background = element_rect(fill = "mediumspringgreen",#Panel color mediumspringgreen
                                        color = "mediumorchid1"),# Border of plot color mediumorchid1
        plot.background = element_rect(fill = "darkblue"))#Plot background is darkblue
ggsave(here("Week_7", "Output", "bad_plot.png"), #Save the output as bad_plot.png
       width = 7, height = 5)

  
```

### **Discussion of why this is a bad plot: ** ###
* The plot is not clear in what it is trying to emphasize. It is unclear what the purpose of the plot is and what it is trying to capture. 
* There is no titles and no labels for the y-axis. There is only a label for the x-axis
* Even though there is a label on the x-axis, there is way too many labels and the text is overlapping with each other. It is also overlapping each other too much and even hard to make out the words in the plot. 
* It is hard to see the colors that correspond to the legend due to the background image of wine. 
* Even though the legend says price, it is unclear exactly what this price is referring too. It is very vague and open to intepretation.

### Good Plot ###

```{r, message=FALSE,warning=FALSE, echo=FALSE}
wine_ratings_good <- wine_ratings %>% #Brining dataframe wine_ratings_good
  drop_na(price) %>% #Drop NA's in price
  select(country, points, price, variety, winery) %>% #Only selecting certain variables in column to work with
  filter(country == "US") %>% #Filter  only to show US country
  group_by(price) #Group_by price

wine_ratings_good %>% 
  ggplot(mapping = aes(x = points,# x-axis is points
                       y = price, #y-axis is price
                       color = points))+ #give color according to price
  geom_bar(stat = "identity")+ #Geometry point, geom_bar
  theme(title = element_text(size = 12, #Editing the theme of graph
                                  color = "red1"))+ #Giving color to title, x-axis and y-axis
  labs(title = "A higher rating for wine doesn't equate to an expensive wine", #Give title
       x = "Wine Ratings", #Labeling x-axis
       y = "Price per bottle [USD]", #Labeling y-axis
       color = "Points",
       subtitle = "Based on the United States Wine rating", #Giving subtitle
       caption = "Source: Kaggle") #Giving caption
ggsave(here("Week_7", "Output", "goodplot.png"),#Save outputs here
       width =7, height = 5)
```
**Discussion of why this is a good plot **
* Clear with plot titles, x-axis, and y-axis labeled
* There are no overlapping aesthetics that may make it hard to see the data
* The title of data explains clearly the purpose and intent of what the data is trying to display

