---
title: "Week 7 Introduction to Mapping"
author: "Sally Heo"
date: "3/8/2022"
output:
  prettydoc::html_pretty:
  theme: tactile
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#### Load libraries needed to code ####
```{r}
library(tidyverse) #Load tidyverse
library(here) #Load here
library(maps) #Load maps
library(mapdata) #Load mapdata
library(mapproj) #Load mapproj
```

# Load the data #
```{r}
popdata<-read_csv(here("Week_7","Data","CApopdata.csv")) #Read in data on population in California by county
stars<-read_csv(here("Week_7","Data","stars.csv")) #Read in data on number of seastars at different field sites

```
# View the data #

```{r}
glimpse(popdata) #View popdata
glimpse(stars) #View stars
```
# Data analysis #

```{r}
world <- map_data("world") #get data for the entire world
head(world)
usa <- map_data("usa") #get mapdata for the USA, extract polygons for different countries
head(usa)
italy <- map_data("italy") #get mapdata for italy
head(italy)
states <- map_data("state") #get data for states
head(states)
counties <- map_data("county") #get data for countries
head(counties)
```
# Make a map of the world #
```{r}
ggplot()+
  geom_polygon(data = world, #Map the data to the world
               aes(x = long, #Plotting x-axis to Long
                   y = lat, #Plotting y-axis to latitude
                   group = group, #To map it nicely
                   fill = region), #add color to region
               color = "black") + #add color to map, black (add color to the lines and fill)
  guides(fill = FALSE) +
  theme_minimal() + #theme minimal, change visuals
  theme(panel.background = element_rect(fill = "lightblue")) + #Make the ocean blue
  coord_map(projection = "mercator", #change the map projection to mercator
            xlim = c(-180,180))
```
# Let's make a map of just california #
```{r}
CA_data<-states %>% #Use the states dataset
  filter(region == "california")#Filter out just the California state
```

# Map of California #
```{r}
ggplot()+
  geom_polygon(data = CA_data,#Map data to California
               aes(x = long, y = lat, group = group), #x-axis long, y-axis lat
               color = "black") + #Add color to map, borders and fill
  coord_map()+
  theme_void()#theme void
  
                   
```

# Adding multiple layers of data, Look at the county data
```{r}
head(counties)[1:3,]#Only showing the first 3 rows for space
```

```{r}
head(popdata) #Look at the county data
```
# Adding multiple layers of data - Wrangle the data #
# Make the column names the same to join the two datasets #
```{r}
CApop_county<-popdata %>% #Using CApop_country
  select("subregion" = County, Population) %>% #rename the county col
  inner_join(counties) %>% #wrangle data, bringing together
  filter(region == "california")#some counties have same names in other states
head(CApop_county)
```

# Map of CA by population by county #
```{r}
ggplot()+
  geom_polygon(data = CApop_county, #Map the CApop county
               aes(x = long, #x-axis long
                   y = lat, #y-axis lat
                   group = group, #Make map look nice
                   fill = Population), #Fill with population
               color = "black")+ #Add color to the map with borders and fill
  geom_point(data = stars,#data for stars, add a point at all my sites
             aes(x = long, #x-axis longitude
                 y = lat, #y-axis latitude
                 size = star_no))+ #Make points proportional to number of stars
  coord_map()+
  theme_void()+
  scale_fill_gradient(trans = "log10")+ #Make it log scale for easier interpretation
  labs(size = "# stars/m") #Make a better legend label
ggsave(here("Week_7", "Output", "CApop.pdf")) #Save it