---
title: "Untitled"
author: "Sally Heo"
date: "4/28/2022"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries needed to code ##
```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(tidyverse) #Load tidyverse
library(here) #Load here
library(palmerpenguins)#Load palmerpenguins
library(broom) #Load broom
library(performance) #Load performance
library(modelsummary) #Load modelsummary
library(tidymodels) #Load tidymodels
```

## Model the penguin dataset ##
* We have tidied and visualized the data and have our set of hypotheses that we want to test
* We can start modeling
```{r}
# Linear model of Bill depth ~ Bill length by species
Peng_mod<-lm(bill_length_mm ~ bill_depth_mm*species, data = penguins)
# check model assumptions with performance
check_model(Peng_mod) #check assumptions of an lm model
anova(Peng_mod) #View results: base R
summary(Peng_mod)#View coefficients (effect size) with error
```
## View results with broom ##
* Using broom we can "tidy" results so that it is easier to view and extract
* Functions glance (), tidy(), augment () will clean up your results
```{r}
# Tidy coefficients
coeffs <- tidy(Peng_mod) #just put tidy() around it
coeffs
#tidy r2, etc
results <- glance(Peng_mod)#glance extracts R-squared, AIc's etc of the model
results
#tidy residuals, etc
resid_fitted <- augment(Peng_mod)
resid_fitted
```
## Results in {modelsummary} ##
* Export summary tables to word, markdown, or tex document. You can also modify the tables to make them pub quality. 
```{r}
# New model
Peng_mod_noX <- lm(bill_length_mm ~ bill_depth_mm, data = penguins)
#Make a list of models and name them
models<-list("Model with interaction" = Peng_mod,
             "Model with no interaction" = Peng_mod_noX)
#Save the results as a .docx
modelsummary(models, output = here("Week_13","output","table.docx"))
```
## Modelplot ##
```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(wesanderson)
modelplot(models) +
    labs(x = 'Coefficients', 
         y = 'Term names') +
    scale_color_manual(values = wes_palette('Darjeeling1'))
```
## Many models with purr, dplyr, and broom ##
```{r}
models<- penguins %>%
  ungroup()%>% # the penguin data are grouped so we need to ungroup them
    nest(-species) %>% # nest all the data by species
  mutate(fit = map(data, ~lm(bill_length_mm~body_mass_g, data = .)))
models
models$fit #shows you each of the 3 models
```
```{r}
results <- models %>% 
  mutate(coeffs = map(fit, tidy),#look at the coefficients
         modelresults = map(fit, glance)) %>% #R2 and others
  select(species, coeffs, modelresults) %>% # only keep the results
  unnest() #put it back in a dataframe and specify which columns to unnest
view(results)#view the results
```
## Tidymodels ##
```{r}
linear_reg()#linear regression
```
```{r}
#Pipe to a plot 
lm_mod <- linear_reg() %>% 
  set_engine("lm") %>% #set the engine for what type of linear regression we are modeling, OLS regression
  fit(bill_length_mm ~ bill_depth_mm*species, data = penguins) %>% #Add model fit
  tidy() %>% #Add the tidy it, now we can pipe this into plots, etc. Nice, tidy way to model
  ggplot()+
  geom_point(aes(x = term, y = estimate))+
  geom_errorbar(aes(x = term, ymin = estimate-std.error,
                    ymax = estimate+std.error), width = 0.1)+
  coord_flip()
lm_mod
```




