---
title: 'Week13: Iterative coding'
author: "Sally Heo"
date: "4/26/2022"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    theme: journal
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries needed to code ##
```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse) #Load tidyverse
library(here) #Load here
```
## Simple for loop ##
* An example of a simple for loop telling us what year it is along a sequence of years
```{r}
print(paste("The year is", 2000)) #Simple code for one year
years <- c(2015:2021) #Put it in a for loop
for (i in years){ #set up the for loop where i is the index
  print(paste("The year is", i)) #loop over i
}
```

```{r}
#Pre-allocate space for the for loop
# empty matrix
year_data <- data.frame(matrix(ncol = 2, nrow = length(years)))
# add column names
colnames(year_data) <- c("year", "year_name")
year_data
```

## Load Data ##
* Using loops to read in multiple .csv files
```{r}
testdata<-read_csv(here("Week_13", "Data", "cond_data", "011521_CT316_1pcal.csv"))
glimpse(testdata)
# point to the location on the computer of the folder
CondPath <- here("Week_13", "Data", "cond_data") #list files in a directory
# list all the files in that path with a specific pattern
# In this case we are looking for everything that has a .csv in the filename

#you can use regex to be more specific if you are looking for certain patterns
files <- dir(path = CondPath,pattern = ".csv")
files

```
## pre-allocate space for the loop ##
* calculating the mean temperature and salinity from each file and saving it
```{r}
# pre-allocate space
# make an empty dataframe that has one row for each file and 3 columns
cond_data <- data.frame(matrix(nrow = length(files), ncol = 3))
# give the dataframe column names
colnames(cond_data) <- c("filename", "mean_temp", "mean_sal")
cond_data
```
## for loop ##
* write basic code to calculate a mean and build out
```{r}
raw_data <- read_csv(paste0(CondPath, "/",files[1]))#test by reading in the first file and see if it works
head(raw_data)
for (i in 1:length(files)){ # loop over 1:3 the number of files (Turn it into a for loop)
  
}
raw_data<-read_csv(paste0(CondPath, "/", files[i])) #Add in the loop over the raw data
glimpse(raw_data)
class(raw_data)
cond_data$filename[i] <- files[i] #Add in the columns, first add in the filename for each row
cond_data$mean_temp[i] <- mean(raw_data$Temperature, na.rm =TRUE)#Add in means for temp
cond_data$mean_sal[i] <- mean(raw_data$Salinity, na.rm =TRUE) #Add in means for salinity
```
## Simple example ##
* There are three ways to do the same thing in a map() function
* First, using a canned function that already exists (calculating the mean from a set of random numbers) and do it 10 times
* create a vector from 1:10
```{r}
1:10 # a vector from 1 to 10 (we are going to do this 10 times)
# for each time 1:10, make a vector of 15 random numbers based on a normal distribution
1:10 %>% # a vector from 1 to 10 (we are going to do this 10 times) %>% # the vector to iterate over
  map(rnorm, n = 15) %>% #calculate 15 random numbers based on a normal distribution in a list
  map_dbl(mean) # calculate the mean from each list. It is now a vector which is type "double"
# Same thing different notation, make your own function...
# Make your own function
1:10 %>% # list 1:10
  map(function(x) rnorm(15,x)) %>% # make your own function
  map_dbl(mean)
# Use a formula when you want to change the arguments within the function
1:10 %>% 
  map(~ rnorm(15, .x)) %>% #changes the arguments inside the function
  map_dbl(mean)
```
## Bring in files using purr instead of a for loop ##
* Reminder: find the files
```{r}
# point to the location on the computer of the folder
CondPath <- here("Week_13", "data", "cond_data")
files <- dir(path = CondPath,pattern = ".csv")
files
# Or..we can get the full file names in one less step by doing this...
files <- dir(path = CondPath,pattern = ".csv", full.names = TRUE)
#save the entire path name
files
# read ub tge files
# Now, read in the files using map instead of a for loop while retaining the filename as a column
data<-files %>% 
  set_names() %>% #set's the id of each list to the file name
  map_df(read_csv,.id = "filename") %>% #map everything to a dataframe and put the id in a column called filename
  group_by(filename) %>% 
  summarise(mean_temp = mean(Temperature, na.rm = TRUE),#calculating means by using group_by filename and summarize
            mean_sal = mean(Salinity,na.rm = TRUE))# calculating mean salinity
data
```

