---
title: 'Week 7: Meteorites Homework'
author: "Sally Heo"
date: "3/8/2022"
output:
  prettydoc::html_pretty:
    theme: tactile
---
# Introduction #
For this homework assignment, we practiced creating a map using the Meteorites datasets from Tidy Tuesday. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries needed to code #
```{r, message=FALSE}
library(tidyverse) #Load tidyverse
library(here) #Load here
library(maps) #Load maps
library(mapdata) #Load mapdata
library(mapproj) #Load mapproj
```

# Load Data #

We are reading the Meteorites dataset from Tidy Tuesday
```{r, warning=FALSE, message=FALSE, results="hide", fig.show="hide"}
meteorites <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-06-11/meteorites.csv")
glimpse(meteorites)#View Meteorites Data
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, results="hide"}
meteorites %>% #Brining Meteorites dataframe to use
  drop_na() #Drop NAs
View(meteorites) #View Meteorites dataset
```

# Make a map of the world (1st step) #
```{r, echo = FALSE, warning = FALSE, message = FALSE, results="hide"}
world <- map_data("world") #get data for the entire world
head(world)
ggplot()+ #creating the base for the world map
  geom_polygon(data = world,#Using geometry point, polygon using world data
               aes(x = long,#x-axis is long
                   y = lat,#y-axis is lat
                   group = group,#Set group to group
                   fill = region),#Fill the region of map
               color = "black")+ #Adding black borders to map
  guides(fill = FALSE)+ #Removing legend for fill
  theme_minimal()+ #Set theme to minimal
  theme(panel.background = element_rect(fill = "lightblue"))+ #Make background ocean blue
  coord_map(projection = "mercator",#changing projection to mercator
            xlim = c(-180, 180))#Setting the limits of x-axis


```

# Adding the Meteorites Data to the World Map #
```{r, echo = FALSE, warning = FALSE, message = FALSE, results="hide"}
ggplot()+ #Using the base world map code
  geom_polygon(data = world,#Adding geometry point, geom polygon
               aes(x = long,#x-axis is long
                   y = lat,#y-axis is lat
                   group = group),#Setting group to group
               fill = "gray", #Fill the map and everything in gray
                   color = "black")+ #Adding black borders
  geom_point(data = meteorites, aes(x = long,#x-axis is long
                                    y = lat, #y-axis is lat
                                    size = mass,#Size of the points are according to the mass
                                    color = mass))+ #color of the points according to the mass
  theme(panel.background = element_rect(fill = "lightblue"))+ #Make background ocean lightblue
  coord_map(projection = "mercator", #Setting projection to Mercator
            xlim = c(-180,180))+ #Setting the x-limits
  labs(title = "Meteorite Impacts",#Giving title to map plot
       x = "Long",#x-axis is long
       y = "Lat", #y-axis is lat
       caption = "Source: Meteoritical Society by way of NASA", #Adding source
       color = "Mass (g)", #change legend title
       size = "Mass (g)") #change legend title
ggsave(here("Week_7", "Output", "meteoritehw.png"))
  
