---
title: "Week_12_Lab_Homework"
author: "Sally Heo"
date: "4/26/2022"
output: 
  prettydoc::html_pretty:
    theme: tactile
---

```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Libraries needed to code ##
```{r, include=FALSE, echo=FALSE, message=FALSE}
library(tidyverse) #Load tidyverse
library(here) #Load here
```

## Load Data ##
```{r}
income_mean <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-02-09/income_mean.csv')

```
## Making something into a factor ##
```{r}
fruits<-factor(c("Apple", "Grape", "Banana"))
fruits
```
## factor booby-traps! ##
```{r}
test<-c("A", "1", "2")
as.numeric(test)
test<-factor(test)#convert to factor
as.numeric(test)
```
## {forcats} ##
```{r}
glimpse(starwars)
```
## starwars data ##
* Looking at how many individuals of each species are present across all starwars films?
```{r}
starwars %>% 
  filter(!is.na(species)) %>% #remove the NAs
  count(species,sort = TRUE)
star_counts <- starwars %>% 
  filter(!is.na(species)) %>% 
  mutate(species = fct_lump(species, n = 3)) %>% 
  count(species)
star_counts
#Order is not in alphabetical order because it is now a factor
```
## Reordering factors - A basic ggplot ##
```{r}
star_counts %>% 
  ggplot(aes(x = species, y = n))+
  geom_col()
# This would be more helpful to view in order of lowest to highest
```
## Reordering factors ##
* A basic ggplot, in order
* Also making it descending
```{r}
star_counts %>% 
  ggplot(aes(x = fct_reorder(species, n, .desc = TRUE), y = n))+ #reorder the factor of species by n, make it descending
  geom_col()+ #Geometry column
  labs(x = "Species") #Label  x-axis as Species
```
## Reordering line plots ##
* Making a line plot and reordering the legend to match the order of the lines
```{r}
glimpse(income_mean)
```
```{r}
glimpse(income_mean)
total_income<-income_mean %>%
  group_by(year, income_quintile)%>%
  summarise(income_dollars_sum = sum(income_dollars))%>%
  mutate(income_quintile = factor(income_quintile)) # make it a factor
```
## Basic line plot ##
* Notice the legend order... Would be more helpful if it is sorted
* reorder line plots by using fct_reorder2, which reorders the data by two variables
```{r}
total_income %>%
ggplot(aes(x = year, y = income_dollars_sum, color = fct_reorder2(income_quintile,year,income_dollars_sum)))+
  geom_line()+
  labs(color = "income quantile")
```
## Reorder levels directly in a vector ##
* Putting in a specific order the way we want (or say)
```{r}
x1 <- factor(c("Jan", "Mar", "Apr", "Dec"))
x1
x1 <- factor(c("Jan", "Mar", "Apr", "Dec"), levels = c("Jan", "Mar", "Apr", "Dec"))
x1
```
## subset data with factors ##
```{r}
starwars_clean <- starwars %>%
  filter(!is.na(species)) %>% # remove the NAs
  count(species, sort = TRUE) %>%
  mutate(species = factor(species)) %>% # make species a factor
  filter(n>3) # only keep species that have more than 3
levels(starwars_clean$species)
  
```

```{r}
starwars_clean<-starwars %>% 
  filter(!is.na(species)) %>% # remove the NAs
  count(species, sort = TRUE) %>%
  mutate(species = factor(species)) %>% # make species a factor 
  filter(n>3)  %>% # only keep species that have more than 3 
  droplevels() # drop extra levels
levels(starwars_clean$species)
```
## recode levels ##
```{r}
starwars_clean<-starwars %>% 
  filter(!is.na(species)) %>% # remove the NAs
  count(species, sort = TRUE) %>%
  mutate(species = factor(species)) %>% # make species a factor 
  filter(n>3)  %>% # only keep species that have more than 3 
  droplevels() %>% # drop extra levels 
  mutate(species = fct_recode(species, "Humanoid" = "Human"))
starwars_clean
```



